---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Rduinoiot

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/Rduinoiot)](https://CRAN.R-project.org/package=Rduinoiot)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/FlavioLeccese92/Rduinoiot/workflows/R-CMD-check/badge.svg)](https://github.com/FlavioLeccese92/Rduinoiot/actions)
<!-- badges: end -->

<<<<<<< HEAD
**Rduinoiot** provides an easy way to connect to [Arduino Iot Cloud API](https://create.arduino.cc/iot/) with R.
Functions allows to exploit [API methods](https://www.arduino.cc/reference/en/iot/api) for many purposes, manage your Arduino devices and dashboards and access to the data produced by sensors and sketches.
=======
{Rduinoiot} provides an easy way to connect to (Arduino Iot Cloud API)[https://create.arduino.cc/iot/] with R.
Functions allows to exploit (API methods)[https://www.arduino.cc/reference/en/iot/api] for many purposes, manage your Arduino devices and dashboards and access to the data produced by sensors and sketches.
>>>>>>> d73c5479c2362f38b8852163bb6b42911991b7c2

## Installation

You can install the development version of Rduinoiot from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("FlavioLeccese92/Rduinoiot")
```
## List things associated to the user

<<<<<<< HEAD
Things associated to the user account can be easily accessed using  `things_list()`.
This function will return detailed information, in particular `things_id` which are needed to access to properties.
=======
Things associated to the user account can be easily accessed using \code{things_list()}. 
This function will return detailed information, in particular \code{things_id}s which are needed to access to properties.
>>>>>>> d73c5479c2362f38b8852163bb6b42911991b7c2

```{r example 1}
library(Rduinoiot)
# Sys.setenv(ARDUINO_API_CLIENT_ID = 'INSERT CLIENT_ID HERE')
# Sys.setenv(ARDUINO_API_CLIENT_SECRET = 'INSERT CLIENT_SECRET HERE')
create_auth_token()

<<<<<<< HEAD
things_list()
=======
dt = things_list()
>>>>>>> d73c5479c2362f38b8852163bb6b42911991b7c2
```

## Real-time sensor data

Reading real-time humidity sensor of one of your devices can be done like this:

```{r example 2}
thing_id = "b6822400-2f35-4d93-b3e7-be919bdc5eba"
property_id = "d1134fe1-6519-49f1-afd8-7fe9e891e778"

things_properties_timeseries(thing_id = thing_id, property_id = property_id,
                             desc = FALSE, interval = 60)
```

